\documentclass[answers]{exam}
\usepackage[utf8]{inputenc}
\usepackage{graphics}
\usepackage{graphicx}
\graphicspath{ {./images/} }
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage[export]{adjustbox}
\usepackage{hyperref}
\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    filecolor=magenta,      
    urlcolor=blue,
}
\urlstyle{same}
\graphicspath{ {./images/} }
\everymath{\displaystyle}

\title{Networks, Games, and Collective Behaviour}
\author{Project proposal}
\date{30 March 2022}

\begin{document}
\maketitle
\paragraph{}
\paragraph{}
\paragraph{}
\paragraph{}
\paragraph{}
\paragraph{}
\begin{center}
    \textbf{Glamour or revulsion: A social analysis of HBO's Euphoria's influence on viewers' drug awareness and habits}
\end{center}
\newpage
\tableofcontents
%\listoffigures

\newpage
\pagebreak
\hspace{0pt}
\vfill
\begin{center}
    "\textit{The sociology of knowledge concerns the analysis of the social structures of reality.}"
\end{center}
\flushright
-Peter L. Berger
\vfill
\hspace{0pt}
\flushleft
\pagebreak

\section{Introduction \& Logistics}

\paragraph{Section:} L1 - Dr. Shah Jamal Alam
\paragraph{Group Members}
\paragraph{}
*All names appear in alphabetical order, any other apparent pattern is purely coincidental.
\begin{enumerate}
    \item Faiz Haseeb - fh06224
    \item Maaz Saeed - ms05050
    \item Shayan Ahmed Shariff - ss05582
\end{enumerate}

\paragraph{}
\paragraph{Overview}

\paragraph{}
HBO's hit show, Euphoria, sees a group of teenagers battle with addiction, self-loathing, and identity issues. In a story which opens with the protagonist lying on the floor, foaming at the mouth from an overdose of illicit drug use, the production team aims to bring to light the consequences, and often ignored dangers of substance abuse.

\paragraph{}
\begin{center}
    "\textit{Equally addictive is the show’s cinematography.}"
\end{center}
\flushright -Divya, K. Bhavani, The Hindu

\paragraph{} \flushleft
In the contemporary world of competitive media, HBO had to bring something special to the table, more than your average teenage-centered series. The hit television show boasts cinematography unmatched by its competitors. From it's \textit{drug-induced} visuals, to it's seamless transitions and imagery which is an ode to famous art history. Consequently, the popularity invoked by such filming techniques has sparked controversy and debate; the vibrant pictorial endeavour is often said to have glamourized the recreational use of drugs with it's narration of partying, sex, and rebellion.
\\

\paragraph{}
Our project aims to identify and study a friendship network, based on viewership of Euphoria. We will divide the people within the network into three subgroups: those who found their curiosity about a certain drug(s) piqued, those who remained indifferent, and those who shied away from drug use, wary of the dangers and risks portrayed by the show. From here onward, we will analyze the nature of links in the social network, examining the existence of characteristics such as peer pressure, social influence of popular agents, not wanting to be isolated, and \textit{homophily}, in terms of of viewership within groups of friends; phenomena such as \textit{triadic} closures and clustering among members of the aforementioned subgroups; and the nature of links between the three groups (for example, does the show bring together all viewers alike, or are there bridges between different groups).

\newpage
\section{Relevant references}
\paragraph{}
\paragraph{}
"D.A.R.E. Is Not a Fan of 'Euphoria'" -- \href{https://www.papermag.com/euphoria-hbo-dare-2656482879.html?rebelltitem=1#rebelltitem1}{PaperMag}
\paragraph{}
\paragraph{}
'Does HBO’s ‘Euphoria’ Really Glamorize Drug Abuse?' -- \href{https://www.forbes.com/sites/danidiplacido/2022/01/29/does-hbos-euphoria-really-glamorize-drug-abuse/?sh=55e3c6d362a9}{Forbes}
\paragraph{}
\paragraph{}
'Reality Television Programs Are Associated With Illegal Drug Use and Prescription Drug Misuse Among College Students' -- \href{https://www.tandfonline.com/doi/abs/10.3109/10826084.2015.1082593}{Taylor \& Francis Online}


\end{document}